\Large\textsc{Regression And Resampling Techniques \\ FYS-STK4155 \\ Assignment One}

### 2019-09-24 assignment_one/article/main.tex
Working on lasso and ridge

  \begin{table}
    \caption{}
    \label{tab:ols_confidence}
  \end{table}
  \section{Terrain Data}

@@

>>>>

  \begin{table}
		\begin{tabular}{llllllr}
	\toprule
	{\(d\)} &    2 &         3 &         4 &         5 \\
	\midrule
	$1$       & \num{5.315e-05} & \num{6.349e-05} & \num{7.072e-05} & \num{6.696e-05} \\[1em]
	$x$       & \num{4.673e-04} & \num{1.682e-03} & \num{4.398e-03} & \num{8.402e-03} \\
	$y$       & \num{4.673e-04} & \num{1.683e-03} & \num{4.396e-03} & \num{8.400e-03} \\[1em]
	$x^2$     & \num{3.686e-04} & \num{6.458e-03} & \num{4.694e-02} & \num{1.959e-01} \\
	$x y$     & \num{2.948e-04} & \num{4.106e-03} & \num{2.873e-02} & \num{1.195e-01} \\
	$y^2$     & \num{3.686e-04} & \num{6.460e-03} & \num{4.692e-02} & \num{1.959e-01} \\[1em]
	$x^3$     &       {} & \num{2.575e-03} & \num{8.868e-02} & \num{9.884e-01} \\
	$x^2 y$   &       {} & \num{1.985e-03} & \num{5.199e-02} & \num{5.432e-01} \\
	$x y^2$   &       {} & \num{1.985e-03} & \num{5.199e-02} & \num{5.429e-01} \\
	$y^3$     &       {} & \num{2.575e-03} & \num{8.864e-02} & \num{9.884e-01} \\[1em]
	$x^4$     &       {} &       {} & \num{2.084e-02} & \num{1.078e+00} \\
	$x^3 y$   &       {} &       {} & \num{1.585e-02} & \num{6.287e-01} \\
	$x^2 y^2$ &       {} &       {} & \num{1.528e-02} & \num{5.443e-01} \\
	$x y^3$   &       {} &       {} & \num{1.585e-02} & \num{6.285e-01} \\
	$y^4$     &       {} &       {} & \num{2.083e-02} & \num{1.078e+00} \\[1em]
	$x^5$     &       {} &       {} &       {} & \num{1.658e-01} \\
	$x^4 y$   &       {} &       {} &       {} & \num{1.253e-01} \\
	$x^3 y^2$ &       {} &       {} &       {} & \num{1.193e-01} \\
	$x^2 y^3$ &       {} &       {} &       {} & \num{1.192e-01} \\
	$x y^4$   &       {} &       {} &       {} & \num{1.253e-01} \\
	$y^5$     &       {} &       {} &       {} & \num{1.658e-01} \\
	\bottomrule
	\end{tabular}
	\caption{The variance of the model parameters \( beta \) with respect
		to the polynomial degree \( d \). The corresponding basis
		function is displayed to the left. Note in particular how the
		variance of the model parameters seems to increase with the
		polynomial degree, which is what is to be expected according to
	the \emph{bias-variance tradeoff}.}
    \label{tab:ols_confidence}
  \end{table}

  \subsubsection{Ridge and Lasso regression}

  We now incorporate Ridge and Lasso regression in our numerical experiments.
  We are still working with the noisy sampled data.

  \section{Terrain Data}

@@

  A study on least-squares surfaces using LR B-splines for representing terrain
  data was presented in \cite{skyttLocallyRefinedSpline2015}. Here, regions of
  high discrepancy between the true surface and the approximating surface was
  locally refined until an acceptable tolerance was reached.
